### 2019-11-29 Mathematical Statistics/ms_ch_04.rmd
mathematical statistics, ch4
mathematical statistics, ch4

x <- seq( from = 1.01, to = 1.99, by = 0.001)

@@

@@

@@

@@

>>>>

x <- seq( from = 1.0001, to = 1.999, by = 0.0001)

@@

Analytical Solution: ${\int_{1}^{1.5}}\frac{2}{x^2} = \frac{2}{3}$

@@

f <- function(x) (3/8)*x**2

x <- seq( from = 0, to = 2, by = 0.001)

ggplot(data.table(x, y)) +
   geom_point(aes(x, y), color = "cornflowerblue", size = .6) +
   labs(title = "pdf f(x) = (3/8)*x**2")

a <- cumsum(y) / sum(y)
p <- round( a[x == 1/5], 4 ) * 100

d <- data.table(x, y = a)

ggplot(d) +
   geom_point(aes(x, y), color = "cornflowerblue", size = .6) +
   geom_area(aes(x, y), data = d[x < 1/5], fill = "cornflowerblue", alpha = .3) +
   labs(title = paste("cdf f(x) = 2/x^2, A =", p ))

Numerical Solution: `r p`%

Analytical Solution: ${\int_{0}^{\frac{1}{5}}}\frac{x^3}{8} = \frac{.008}{8} = .001 = .1$ %

@@

z <- (51 - 48) / (9^2 / sqrt(30))
p <- pnorm(z, lower.tail = F)

Probability: __`r round(p, 4)*100`%__

@@

z <- ( .5 - .55 ) / sqrt(.55 * (1 - .55) / 36)

p <- pnorm(z, lower.tail = T)

Probability: `r round(p, 4)*100`%
